Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-05-07 manuscript_results.Rmd
update

# Create a list of data frames for the four weeks
weeks <- 1:4
summed_data_list <- list()

  # Calculate the percentage difference at the row level (i.e., per state-date)
  data__ <- data__ %>%
    mutate(Difference = ((AUTO_AVG_LB / AUTO_AR) - 1) * 100)

  # Group by Julian date and calculate mean and standard deviation of Difference
  summarized <- data__ %>%
    group_by(Julian_date) %>%
    summarize(
      Mean_Diff = Difference,
      SD_Diff = sd(Difference, na.rm = TRUE)
    ) %>%
    mutate(Week = paste0("Week ", week))

  # Store the summarized data
  summed_data_list[[week]] <- summarized
}

@@

# Plot the mean difference with error bars for standard deviation
model_improv <- ggplot(summed_data_all, aes(x = Julian_date, y = Mean_Diff, color = Week)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = Mean_Diff - SD_Diff, ymax = Mean_Diff + SD_Diff), width = 0.5) +
  geom_hline(yintercept = 0, color = "black", linetype = "dashed", size = 0.8) +
  theme_minimal() +
  labs(
    title = "Figure 10: Mean percentage of WIS differences across all states",
    subtitle = "AUTO_AVG_LB compared to baseline",
    x = "",
    y = "Difference (%)"
  ) +
  scale_y_continuous(
    limits = c(-100, 100),
    breaks = seq(-100, 100, by = 20)
  ) +
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b %y"
  ) +
  scale_color_manual(
    values = c("Week 1" = "#ffcccc",
               "Week 2" = "#ff6666",
               "Week 3" = "#cc0000",
               "Week 4" = "#990000")
  ) +
  theme(
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

#ggsave(model_improv, height = 4.5, width = 9, filename = "Fig11.jpg")

>>>>

```{r}
weeks <- 1:4
summed_data_list <- list()

for (week in weeks) {
  # Merge the data frames
  data__ <- merge(get(paste0("filtered_df_W", week, "_NoLg")),
                  get(paste0("filtered_df_W", week)))

  # Step 1: Calculate % difference at state level
  data__ <- data__ %>%
    mutate(Diff_state = ((AUTO_AVG_LB / AUTO_AR) - 1) * 100)

  # Step 2: Aggregate sum of components across states for mean difference
  summed_data <- data__ %>%
    group_by(Julian_date) %>%
    summarize(
      AUTO_AR = sum(AUTO_AR, na.rm = TRUE),
      AUTO_AVG_LB = sum(AUTO_AVG_LB, na.rm = TRUE),
      SD_Diff = sd(Diff_state, na.rm = TRUE)  # SD of raw state-level % differences
    ) %>%
    mutate(
      Difference = ((AUTO_AVG_LB / AUTO_AR) - 1) * 100,  # Mean from totals
      Week = paste0("Week ", week)
    )

  summed_data_list[[week]] <- summed_data
}

@@

model_improv <- ggplot(summed_data_all, aes(x = Julian_date, y = Difference, color = Week)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = Difference - SD_Diff, ymax = Difference + SD_Diff), width = 0.5) +
  geom_hline(yintercept = 0, color = "black", linetype = "dashed", size = 0.8) +
  theme_minimal() +
  labs(
    title = "Figure 10: Mean percentage of WIS differences across all states",
    subtitle = "AUTO_AVG_LB compared to baseline",
    x = "",
    y = "Difference (%)"
  ) +
  scale_y_continuous(
    limits = c(-400, 400),
    breaks = seq(-100, 100, by = 20)
  ) +
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b %y"
  ) +
  scale_color_manual(
    values = c("Week 1" = "#ffcccc",
               "Week 2" = "#ff6666",
               "Week 3" = "#cc0000",
               "Week 4" = "#990000")
  ) +
  theme(
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

model_improv
```
